\textbf{Evaluating RISC-V Enclaves:}\\ Security Without the Slowdown?

### 2025-09-03 draft_presentation.tex
improved PMP diagram

\begin{frame}{QEMU-Based Virtualized Environment}
    \small
    \begin{itemize}
        \item QEMU emulates RISC-V architecture for repeatability and control. \pause
        \item Ensures consistent test conditions by eliminating hardware-induced variations (thermal throttling, cache behavior). \pause
        \item Configured for RV64GC architecture, as required by Keystone. \pause
    \end{itemize}
    \vspace{0.5em}
    \uncover<4->{\textbf{Why QEMU?} Provides a controlled, consistent environment for repeatability.}
\end{frame}

@@

\begin{frame}{PMP Entries vs Max Concurrent Enclaves}
\centering
\begin{figure}[htbp]
\centering
\begin{tikzpicture}
\begin{axis}[
    width=10cm,
    height=6cm,
    xlabel={PMP Entries},
    ylabel={Max Concurrent Enclaves},
    xmin=0, xmax=16,
    ymin=0, ymax=16,
    xtick={0,4,8,12,16},
    ymajorgrids,
    grid style=dashed,
    mark options={solid},
    nodes near coords,
    every node near coord/.append style={font=\footnotesize, /pgf/number format/fixed},
    clip=false,
    cycle list={{teal,mark=*,thick}},
    tick label style={font=\small},
    label style={font=\small\bfseries},
]

@@

% Annotation inside shaded region
\node[red, align=center, font=\footnotesize\bfseries] at (axis cs:12,12) {PMP Exhaustion \\ Caps at 8 Enclaves};

>>>>

% \begin{frame}{QEMU-Based Virtualized Environment}
%     \small
%     \begin{itemize}
%         \item QEMU emulates RISC-V architecture for repeatability and control. \pause
%         \item Ensures consistent test conditions by eliminating hardware-induced variations (thermal throttling, cache behavior). \pause
%         \item Configured for RV64GC architecture, as required by Keystone. \pause
%     \end{itemize}
%     \vspace{0.5em}
%     \uncover<4->{\textbf{Why QEMU?} Provides a controlled, consistent environment for repeatability.}
% \end{frame}

@@

\begin{frame}{PMP Entries vs Max Concurrent Enclaves}
\centering
\begin{figure}[htbp]
\centering
\begin{tikzpicture}
\begin{axis}[
    width=10cm,
    height=6cm,
    xlabel={PMP Entries},
    ylabel={Concurrent Enclaves},
    xmin=0, xmax=16,
    ymin=0, ymax=16,
    xtick={0,4,8,12,16},
    ymajorgrids,
    grid style=dashed,
    mark options={solid},
    nodes near coords,
    every node near coord/.append style={font=\footnotesize, /pgf/number format/fixed},
    clip=false,
    cycle list={{teal,mark=*,thick}},
    tick label style={font=\small},
    label style={font=\small\bfseries},
]

@@

% Add Yellow Sliding Zone (between 4 and 8 PMP entries)
\fill[yellow!30, opacity=0.6] (axis cs:4,0) rectangle (axis cs:8,16);

% Annotation inside shaded region
\node[red, align=center, font=\footnotesize\bfseries] at (axis cs:12,12) {PMP Exhaustion \\ Caps at 8 Enclaves};
\node[align=center, font=\footnotesize\bfseries, text=black] at (axis cs:6,12) {Sliding Zone};
